SPIDERMAN: an open-source code to model phase curves and secondary eclipses

### 2017-08-14 ms.tex
Update on Overleaf.

As well as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter \citep{Rauscher2007}. This technique works because the inclination of the system results in the occulting limb of the star scanning across the disc of the planet in both longitude and latitude during ingress and egress. The brightness distribution of the planet's permanent dayside will be imprinted on the precise shape of the ingress and egress curves. This has been demonstrated for HD\,189733 b by \citep{Majeau2012} ((and others))

@@

For example, if there are two collision points between the outer arc and the edge of the star, then this falls into the case where the occulted area can be described by the sum of two circular segments. Other cases include larger numbers of components, but can still be described by a small number of circle segments and triangles.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{img/all_models.pdf}
		\caption{This alright fit to Xi as a function of wavelength. blue: flat line, green: gradient function, orange: step function}
		\label{fig:best_fit_flux}
	\end{center}
\end{figure}

We test for the dependence of the value of \xi

The flat model gave a value of -0.36 - which is consistent with the white light value. This gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF

@@

The best fitting model was the step function model with a dividing wavelength of 1.4225 microns, and step values of -0.5242412 -0.2149221. This gave a chi2 of 8.0 (R chi2 of 0.62) with 12 DOF.

While we find that there is weak evidence for a trend with wavelength in the data, the flat line model provides a satisfactory fit to the data.

>>>>

As well as longitudinal mapping with phase curves, it is possible to get a two-dimensional map of the dayside of an exoplanet from the secondary eclipse, provided that there is a non-zero impact parameter \citep{Rauscher2006}. This technique works because the inclination of the system results in the occulting limb of the star scanning across the disc of the planet in both longitude and latitude during ingress and egress. The brightness distribution of the planet's permanent dayside will be imprinted on the precise shape of the ingress and egress curves. This has been demonstrated for HD\,189733 b by \citep{Majeau2012} ((and others))

@@

For example, if there are two collision points between the outer arc and the edge of the star, then this falls into the case where the occulted area can be described by the sum of two circular segments. Other cases include larger numbers of components, but can still be described by a small number of circle segments and triangles, a list of the major classes are given below.

An individual segment is defined as having an inner and outer circle edge, and a first and second "outer" edge, which is the radial line from the center of the planet.

\subsubsection{Case 1: zero collisions}
The trivial case where the segment is either entirely blocked, or entirely unobscured. If the distance from the center of the segment to the center of the star is less than the stellar radius then the entire area is added, otherwise nothing is.

\subsubsection{Case 2: Inner and outer circles crossed once}
The case where both the inner and outer circle segments are both intersected by the disc of the star, and the straight edges are untouched. In this case the total area is calculated as follows
\begin{equation} \label{eq:inner_outer}
A_{tot} = A_1 + A_2 + A_3 - A_4
\end{equation}
$A_1$ is the circle segment of the stellar disc bounded by the intersection points with the inner and outer circles. $A_2$ is the circle segment of the outer circle edge bounded by the intersection point with the stellar disc and the first straight edge. $A_3$ is the quadrilateral with the edges defined by the two intersection points and the end points of the straight edge that is within the stellar disc. $A_4$ is the circle segment of the circle segment of the inner circle edge bounded by the intersection point with the stellar disc and the straight edge.

\subsubsection{Case 3: Inner and outer circles crossed once, one straight edge crossed twice.}

\begin{equation} \label{eq:inner_outer}
A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
\end{equation}

This is calculated the same as Case 2, but an additional area element is subtracted, $A_5$, which is the circle segment formed by the disc of the star and the two intersection points with the straight edge.

\subsubsection{Case 4: inner edge crossed twice, both straight edges crossed.}

this one has two subcases

\begin{equation} \label{eq:inner_outer}
A_{tot} = A_1 + A_2 - A_3 - A_4 - A_5 - A_6
\end{equation}

$A_1$ is the area of the triangle formed by the contact point and two corners interior to the stellar disc. $A_2$ is

\begin{equation} \label{eq:inner_outer}
A_{tot} = A_1 + A_2 + A_3 - A_4 - A_5
\end{equation}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{img/all_models.pdf}
		\caption{The values of log($\xi$) as a function of wavelength. Several simple models are fit to the data to test for wavelength dependence. A flat line in blue, a gradient model in green and a step function in orange.}
		\label{fig:best_fit_flux}
	\end{center}
\end{figure}

We test if there is a significant dependence of the value of $\log(\xi)$ on the wavelength by attempting to fit several simple models to the data. The null model, which assumes there is no dependence on wavelength is simply a flat line. This model gave an acceptable fit, with a chi2 of 15.1 (R chi2 of 1.16) with 14 DOF with a best fitting value of -0.36 - which is consistent with the white light value.

@@

A function approximating a step function might be expected, since the wavelength region covers the water band;values inside the water band will probe lower pressures than those outside, due to the increased optical depth. To test for such a feature, we use a step function with three parameters: $\delta_{out}$, which is the average value outside of the step function, $\delta_{in}$ which is the value on the other side of the step, and $\gamma$, which is the wavelength which separates the two sides of the step function. The best fitting model was found to have $\gamma$ of 1.4225 microns, which is close to what would be expected for a water features, $\delta_{out}$ of -0.5242412 and $\delta_{in}$ of -0.2149221. This model gave a chi2 of 8.0 (R chi2 of 0.62) with 12 DOF.

Using a Bayesian Information Criterion, the improvement of chi2 is marginal for the gradient model and the step function model, and not enough to constitute significant evidence in favour of either model, so we prefer the interpretation of a flat line. While we find that there is weak evidence for a trend with wavelength in the data, the flat line model provides a satisfactory fit to the data. A full treatment would require calculating the pressure contribution function for each wavelength as was done in \citet{Stevenson2014}, which is beyond the scope of this work.
